A Linear Solution of the Linearity Challenge

### 2025-12-25 paper/abstract.tex
expanded abstract

\abstract{%
    We describe the Agda formalisation of a process calculus based on classical
    linear logic that supports the modeling of binary sessions. The
    formalisation turns out to be remarkably compact despite the use of
    ``plain'' context splitting for the proper management of linear channels. We
    argue that the logical nature of the calculus and the use of explicit
    continuations are contributing factors to the simplicity of its
    formalisation.
    %
}

>>>>

\abstract{%
    The formalisation of session calculi is considered challenging due to the
    management of channels, which are linear resources that cannot be discarded
    or duplicated at will and whose type changes over time, as input/output
    operations are performed on them.
    %
    Context splitting, the ``naive'' channel management technique directly
    related to the way session type theories are usually sketched with pen and
    paper, is often considered a hindrance and a notable source of complexity,
    to the point that several alternative approaches have been recently
    proposed.
    %
    In this paper we describe the Agda formalisation of a process calculus based
    on classical linear logic that supports the modeling of binary sessions
    through their encoding with explicit continuation channels. The
    formalisation turns out to be remarkably compact despite the adoption of
    context splitting. We argue that the logical nature of the calculus and the
    use of explicit continuations are contributing factors to the simplicity of
    its formalisation.
    %
}
